MoneyBallR_Modeling

### 2019-09-25 hw1/doc/HW1.Rmd

We *could* make an assumption that these are all cases where there were no batters hit by a pitch, but that seems ill-advised given the distribution above. In this case, we might be wise to leave them as NA for now.

@@

We can use the KNN imputation to help with the NA values

```{r}
impute_me <- is.na(training$TEAM_PITCHING_SO)
training[impute_me,"TEAM_PITCHING_SO"] <- knn[impute_me,"TEAM_PITCHING_SO"] 
```

With the NA's fixed, we can turn our attention now to the extreme values.

@@

We'll make a high-yet-reasonable assumption of a mean 11 innings per game, and call anything more than 5,346 strikeouts an invalid data point by setting them to NA so they will be disregarded in any modeling.

@@

@@

@@

@@

summary(moneyball_test$squared_error)
```

>>>>

We will fill in the values with KNN

```{r}
impute_me <- is.na(training$TEAM_BATTING_HBP)
training[impute_me,"TEAM_BATTING_HBP"] <- knn[impute_me,"TEAM_BATTING_HBP"] 
```

```{r}
training %>% 
  ggplot(aes(TEAM_BATTING_HBP)) + 
  geom_histogram(bins = 50) +
  geom_vline(aes(xintercept = mean(TEAM_BATTING_HBP, na.rm = T)), col = "red", lty = 2) +
  geom_vline(aes(xintercept = median(TEAM_BATTING_HBP, na.rm = T)), col = "green", lty = 2) +
  labs(x = element_blank(),
       y = "Count",
       title = "Distribution of Being Hit By a Pitch",
       subtitle = "After Imputation",
       caption = "* Red line is the mean value and green is the median")
```

@@

We can use the KNN imputation to help with the NA values.  We can turn our attention now to the extreme values.

@@

We'll make a high-yet-reasonable assumption of a mean 11 innings per game, and call anything more than 5,346 strikeouts an invalid data point by setting them to NA so they will be imputed prior to modeling.

@@

impute_me <- is.na(training$TEAM_PITCHING_SO)
training[impute_me,"TEAM_PITCHING_SO"] <- knn[impute_me,"TEAM_PITCHING_SO"]

@@

### Kitchen Sink Model

We will begin with a "kitchen sink" model.

### Select Variables

We will select a subset of variables.

```{r}
fit_final <- lm(TARGET_WINS ~ TEAM_BATTING_H + TEAM_BATTING_BB + TEAM_BATTING_HBP + TEAM_FIELDING_E, data = moneyball_train)
summary(fit_final)
```

@@

In order to select which model is the "best" we will test it against a test set.  We will examine the difference between the predicted and actual.

### Kitchen Sink Selection

@@

summary(moneyball_test$error)
```

### Select Model

```{r}
moneyball_test$y_hat <- predict(fit_final, moneyball_test)
moneyball_test <- moneyball_test %>%
  mutate(error = TARGET_WINS - y_hat) %>%
  mutate(squared_error = error ^ 2)

summary(moneyball_test$error)
```

### 2019-09-25 hw1/results/Exploratory Data Analysis.Rmd

```{r}
training <- training %>%
  mutate(TEAM_PITCHING_SO_flag = ifelse(is.na(TEAM_PITCHING_SO), 1, 0)) %>%
  mutate(TEAM_PITCHING_SO = ifelse(is.na(TEAM_PITCHING_SO), mean(TEAM_PITCHING_SO), TEAM_PITCHING_SO))
```

@@

To fill the the `r nrow(training[is.na(training$TEAM_FIELDING_DP),])` missing values with the mean.

```{r}
training <- training %>%
  mutate(TEAM_FIELDING_DP_flag = ifelse(is.na(TEAM_FIELDING_DP), 1, 0)) %>%
  mutate(TEAM_PITCHING_SO = ifelse(is.na(TEAM_FIELDING_DP), mean(TEAM_FIELDING_DP), TEAM_FIELDING_DP))
```

@@

```{r}
training <- training %>%
  mutate(TEAM_BATTING_SO = -1 * TEAM_BATTING_SO) %>%
  mutate(TEAM_PITCHING_SO = -1 * TEAM_PITCHING_SO) %>%
  mutate(TEAM_PITCHING_H = -1 * TEAM_PITCHING_H) %>%
  mutate(TEAM_FIELDING_E = -1 * TEAM_FIELDING_E) %>%
  mutate_at(scale, .vars = vars(-TARGET_WINS)) %>%
  #mutate(TEAM_BATTING = TEAM_BATTING_H + TEAM_BATTING_2B + TEAM_BATTING_3B + TEAM_BATTING_HR + TEAM_BATTING_BB + TEAM_BATTING_SO) %>%
  mutate(TEAM_BATTING = TEAM_BATTING_H + TEAM_BATTING_BB + TEAM_BATTING_SO) %>%
  mutate(TEAM_PITCHING = TEAM_PITCHING_BB + TEAM_PITCHING_H + TEAM_PITCHING_HR + TEAM_PITCHING_SO) %>%
  mutate(TEAM_FIELDING = TEAM_FIELDING_DP + TEAM_FIELDING_E)
```

@@

@@

```{r}
fit <- lm(TARGET_WINS ~ TEAM_BATTING + TEAM_PITCHING + TEAM_FIELDING, training)
summary(fit)
```

This model says that the average baseball team will win about `r round(coef(fit)[1],0)` games.  If their batting is one standard deviation better than the average they will win `r round(coef(fit)[2],0)` more games.  They will win `r round(coef(fit)[3],0)` more games for if their pitching and `r round(coef(fit)[4],0)` if their fielding is better than average.

>>>>

```{r}
training <- training %>%
  mutate(TEAM_PITCHING_SO_flag = ifelse(is.na(TEAM_PITCHING_SO), 1, 0)) %>%
  mutate(TEAM_PITCHING_SO = ifelse(is.na(TEAM_PITCHING_SO), mean(TEAM_PITCHING_SO, na.rm = TRUE), TEAM_PITCHING_SO))
```

@@

We will fill the the `r nrow(training[is.na(training$TEAM_FIELDING_DP),])` missing values with the mean.

```{r}
training <- training %>%
  mutate(TEAM_FIELDING_DP_flag = ifelse(is.na(TEAM_FIELDING_DP), 1, 0)) %>%
  mutate(TEAM_FIELDING_DP = ifelse(is.na(TEAM_FIELDING_DP), mean(TEAM_FIELDING_DP, na.rm = TRUE), TEAM_FIELDING_DP))
```

### Stolen Bases

Wee will fill the the `r nrow(training[is.na(training$TEAM_BASERUN_SB),])` missing values with the mean.

```{r}
training <- training %>%
  mutate(TEAM_BASERUN_SB_flag = ifelse(is.na(TEAM_BASERUN_SB), 1, 0)) %>%
  mutate(TEAM_BASERUN_SB = ifelse(is.na(TEAM_BASERUN_SB), mean(TEAM_BASERUN_SB, na.rm = TRUE), TEAM_BASERUN_SB))
```

### Caught Stealing Bases

We will fill the the `r nrow(training[is.na(training$TEAM_BASERUN_CS),])` missing values with the mean.

```{r}
training <- training %>%
  mutate(TEAM_BASERUN_CS_flag = ifelse(is.na(TEAM_BASERUN_CS), 1, 0)) %>%
  mutate(TEAM_BASERUN_CS = ifelse(is.na(TEAM_BASERUN_CS), mean(TEAM_BASERUN_CS, na.rm = TRUE), TEAM_BASERUN_CS))
```

@@

```{r}
training <- training %>%
  mutate(TEAM_BATTING_SO = -1 * TEAM_BATTING_SO) %>%
  #mutate(TEAM_PITCHING_SO = -1 * TEAM_PITCHING_SO) %>%
  #mutate(TEAM_PITCHING_H = -1 * TEAM_PITCHING_H) %>%
  #mutate(TEAM_BASERUN_CS = -1 * TEAM_BASERUN_CS) %>%
  #mutate(TEAM_FIELDING_E = -1 * TEAM_FIELDING_E) %>%
  mutate_at(scale, .vars = vars(-TARGET_WINS)) %>%
  #mutate(TEAM_BATTING = TEAM_BATTING_H + TEAM_BATTING_BB + TEAM_BATTING_SO, TEAM_BATTING_HR) %>%
  mutate(TEAM_BATTING = TEAM_BATTING_H + TEAM_BATTING_2B + TEAM_BATTING_3B + TEAM_BATTING_HR + TEAM_BATTING_BB + TEAM_BATTING_SO) %>%
  mutate(TEAM_PITCHING = TEAM_PITCHING_BB + TEAM_PITCHING_H + TEAM_PITCHING_HR + TEAM_PITCHING_SO) %>%
  mutate(TEAM_BASERUN = TEAM_BASERUN_SB + TEAM_BASERUN_CS) %>%
  mutate(TEAM_FIELDING = TEAM_FIELDING_DP + TEAM_FIELDING_E)
```

@@

```{r}
training %>%
  mutate(x = TEAM_BASERUN) %>%
  plot_me(., "Stealing Bases", element_blank(), element_blank())
```

@@

```{r}
fit <- lm(TARGET_WINS ~ TEAM_BATTING, training)
summary(fit)
```

This model says that the average baseball team will win about `r round(coef(fit)[1],0)` games.  If their batting is one standard deviation better than the average they will win `r round(coef(fit)[2],0)` more games.  They will win `r round(coef(fit)[3],0)` more games for if their pitching is better than average.

### 2019-09-25 hw1/results/MoneyBallR_Stepwise_Model_Critical_Thinking_Group_3.Rmd

# Decision Trees to Find Variable Interactions
```{r}
library(tidyverse)
df_train <- read.csv("https://raw.githubusercontent.com/crarnouts/Data_621/master/moneyball-training-data.csv")
df_test <- read.csv("https://raw.githubusercontent.com/crarnouts/Data_621/master/moneyball-evaluation-data.csv")
source("https://raw.githubusercontent.com/crarnouts/Data_605_Final/master/RandomForestNulls_testing.R")
colnames(df_train) <- sub("TEAM_", "", colnames(df_train))
colnames(df_test) <- sub("TEAM_", "", colnames(df_test))
df_test <- RF_with_Nulls(df_train,df_test,"TARGET_WINS",.5,10,25,.02,5,1)
```

# See if we can impute some misssing values Using a Random Forest
```{r}
library(randomForest)
df_train.na <- df_train
df_train.imputed <-rfImpute(TARGET_WINS ~.,df_train.na)
str(df_train)
str(df_train.imputed)
df_train <- df_train.imputed
```

@@

#Principal Components
```{r}
#PCA Analysis in R DataCamp Article
library(tidyverse)
mtcars.pca <- prcomp(mtcars[,c(1:7,10,11)], center = TRUE,scale. = TRUE) #exclude the categorical variables
mtcars <- mtcars 
summary(mtcars.pca)
str(mtcars.pca)
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
ggbiplot(mtcars.pca) # this shows you what attributes contribute to principal component 1 and 2
ggbiplot(mtcars.pca, labels=rownames(mtcars)) # add in the sample information
mtcars.country <- c(rep("Japan", 3), rep("US",4), rep("Europe", 7),rep("US",3), "Europe", rep("Japan", 3), rep("US",4), rep("Europe", 3), "US", rep("Europe", 3))
ggbiplot(mtcars.pca,ellipse=TRUE,  labels=rownames(mtcars), groups=mtcars.country) #represent circles around groupings I want to do this binary classifiers
ggbiplot(mtcars.pca,ellipse=TRUE,choices=c(3,4),   labels=rownames(mtcars), groups=mtcars.country) # take a look at some of the other principal components
################################################################################
##################### Same thing but with MoneyBallR data ######################
################################################################################
df_train.pca <- prcomp(df_train[,c(3:17)], center = TRUE,scale. = TRUE) #exclude the categorical variables
df_train.target <- 
summary(df_train.pca)
str(df_train.pca)
ggbiplot(df_train.pca) + geom_point(size = .01)+ xlim(-8,8)+ ylim(-10,5)
ggbiplot(mtcars.pca,ellipse=TRUE,choices=c(3,4),   labels=rownames(mtcars), groups=mtcars.country) # take a look at some of the other principal components
library(tidyverse)
test <- df_train %>% dplyr::select(BATTING_H)
df_train.pca <- df_train %>% dplyr::select(PITCHING_HR,BATTING_HR) %>%  prcomp(center = TRUE,scale. = TRUE) #exclude the categorical variables
summary(df_train.pca)
str(df_train.pca)
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
ggbiplot(df_train.pca) + geom_point(size = .01)+ xlim(-8,8)+ ylim(-10,5)
ggplot(df_train, aes(x=PITCHING_HR, y=BATTING_HR, colour = TARGET_WINS)) +
    geom_point(shape=1) + 
scale_colour_gradient(low="cyan", high="firebrick1")     # Use hollow circles
df_train$HR_RATIO <- df_train$BATTING_HR/df_train$PITCHING_HR
library(plotly)
ggplotly(ggplot(df_train, aes(x=PITCHING_HR, y=HR_RATIO, colour = TARGET_WINS)) +
    geom_point(shape=1) + 
scale_colour_gradient(low="cyan", high="firebrick1")     # Use hollow circles
)
mid <- mean(df_train$TARGET_WINS)
ggplotly(ggplot(df_train, aes(x=BATTING_H, y=PITCHING_H, colour = TARGET_WINS)) +
    geom_point(shape=1) + 
 scale_color_gradient2(midpoint = mid, low = "blue", mid = "white",
                            high = "red", space = "Lab" )     # Use hollow circles
)
## look at batting hits to pitching hits ratio
df_train$Hitting_Ratio <- df_train$BATTING_H/df_train$PITCHING_H
ggplotly(ggplot(df_train, aes(x=Hitting_Ratio, y=TARGET_WINS, colour = TARGET_WINS)) +
    geom_point(shape=1) + 
 scale_color_gradient2(midpoint = mid, low = "blue", mid = "white",
                            high = "red", space = "Lab" )     # Use hollow circles
)
for (i in 1:ncol(df_train)){
ggplotly(ggplot(df_train, aes(x=df_train[[i]], y=TARGET_WINS, colour = TARGET_WINS)) +
    geom_point(shape=1) + 
 scale_color_gradient2(low = "blue",
                            high = "red", space = "Lab" )     # Use hollow circles
)
}
ggplotly(ggplot(df_train, aes(x=BATTING_2B , y=BATTING_H, colour = TARGET_WINS)) +
    geom_point(shape=1) + 
 scale_color_gradient2(midpoint = mid, low = "blue", mid = "white",
                            high = "red", space = "Lab" ) )
```

#Predict Hits Batted by Hits Pitched and then see what the difference is so like hits batted above expectation
And then use this as a predictive feature

```{r}
#First Fit Target Wins just by Batted_H and Pitched_H
#model <- lm(TARGET_WINS ~ BATTING_H + PITCHING_H, data = df_train)
#df_train$Prediction <- predict(model,df_train)
#summary(model)
## .45 correlation 
##try on it on out of sample
### Add my meta features ###
df_train <- dplyr::filter(df_train,df_train$TARGET_WINS != 0) %>% filter(BATTING_H != 0) %>% filter(BATTING_3B != 0) %>% 
filter(BATTING_2B != 0)%>% filter(BATTING_HR != 0)%>% filter(BATTING_BB != 0)%>% filter(BATTING_SO != 0)
# ## Adding in some new features ##
# df_train$Pitch_HR_under_2 <- ifelse(df_train$PITCHING_HR <2,1,0)
# df_train$Errors_over_1215 <- ifelse(df_train$FIELDING_E > 1215,1,0)
# df_train$HR_RATIO_2 <- (df_train$HR_RATIO)^2
### Add in some new feature engineering 
df_train$BATTING_1B <- df_train$BATTING_H - df_train$BATTING_2B - df_train$BATTING_3B - df_train$BATTING_HR
df_train$BASES_ACQUIRED <- df_train$BATTING_1B + 2*df_train$BATTING_2B + 3*df_train$BATTING_3B + 4*df_train$BATTING_H + df_train$BATTING_BB
train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]
model <- lm(TARGET_WINS ~ ., data = train_data)
hold_out_data$Prediction <- predict(model,hold_out_data)
cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS)
summary(model)
## Non linear benchmark random forest
train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]
hold_out_data <- RF_with_Nulls(df_train,hold_out_data,"TARGET_WINS",.5,4,500,.005,5,10)
cor(hold_out_data$prediction_overall,hold_out_data$TARGET_WINS)
# 
# 
# ############# FITTING THE MODEL WITH EVERYTHING ###################
# ############# BASELINE ############################################
# df_train$INDEX <- NULL
# train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
# train_data<- df_train[ train.index1,]
# hold_out_data  <- df_train[-train.index1,]
# model <- lm(TARGET_WINS ~ ., data = train_data)
# hold_out_data$Prediction <- predict(model,hold_out_data)
# cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS)
# summary(model)
ggplotly(ggplot(hold_out_data, aes(x=Prediction, y=TARGET_WINS, colour = TARGET_WINS)) +
     geom_point(shape=1) + 
  scale_color_gradient2(low = "blue",
                             high = "red", space = "Lab" )     # Use hollow circles
 )
ggplot(data = hold_out_data, aes(x = Prediction, y = TARGET_WINS)) + 
  geom_point(color='blue') +
  geom_smooth(method = "lm", se = FALSE)
toselect.x <- summary(model)$coeff[-1,4] < 0.05 #
relevant.x <- names(toselect.x)[toselect.x == TRUE]

sig.formula <- as.formula(paste("TARGET_WINS ~",paste(relevant.x, collapse= "+")))

model <- lm(formula = sig.formula, data = train_data)
summary(model)
```

##Look at Variance Inflation Factors 
```{r}
df_train1 <- df_train
df_train1$BATTING_H <- NULL
df_train1$BATTING_SO<- NULL
df_train1$HR_RATIO <- NULL
df_train1$BASES_ACQUIRED <- NULL
df_train1$Hitting_Ratio <- NULL
df_train1$PITCHING_HR <- NULL
for (i in 3:ncol(df_train1)){
col <- noquote(paste(colnames(df_train1)[i],"~ ."))
model <- lm(col, data = df_train1)
r_squared <- summary(model)$adj.r.squared
VIF <- 1/(1-(r_squared))
print(colnames(df_train1)[i])
print(VIF)
#print(summary(model))
}
```

```{r}
train.index1 <- createDataPartition(df_train1$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]
model <- lm(TARGET_WINS ~ BATTING_BB + BATTING_SO + BASERUN_CS + PITCHING_HR + 
    PITCHING_BB + PITCHING_SO + FIELDING_E + FIELDING_DP + I(BATTING_2B^2) + 
    I(BATTING_3B^2) + I(BATTING_BB^2) + I(BATTING_SO^2) + I(BASERUN_SB^2) + 
    I(BASERUN_CS^2) + I(PITCHING_H^2) + I(PITCHING_BB^2) + I(PITCHING_SO^2) + 
    I(FIELDING_E^2) + I(FIELDING_DP^2) + I(BATTING_1B^2) + 
    I(BATTING_2B^3) + I(BATTING_3B^3) + I(BATTING_HR^3) + I(BATTING_SO^3) + 
    I(BASERUN_CS^3) + I(PITCHING_H^3) + I(PITCHING_BB^3) + I(FIELDING_E^3) + 
    I(FIELDING_DP^3) + I(BATTING_2B^4) + I(BATTING_3B^4) + I(BATTING_HR^4) + 
    I(BATTING_BB^4) + I(BATTING_SO^4) + I(BASERUN_CS^4) + I(PITCHING_H^4) + 
    I(PITCHING_BB^4) + I(FIELDING_E^4) + I(FIELDING_DP^4) + I(BATTING_1B^4), data = df_train)
hold_out_data$Prediction <- predict(model,hold_out_data)
cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS)
summary(model)
```

#Poisson GLMS
```{r}
df_train$INDEX <- NULL
train.index1 <- createDataPartition(df_train1$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]
# Poisson Regression
# where count is a count and
# x1-x3 are continuous predictors
fit <- glm(TARGET_WINS ~ ., data = train_data, family=poisson())
summary(fit)
hold_out_data$Prediction <- predict(fit,hold_out_data)
cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS)
```

#Stepwise Regression
```{r}
train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]

@@

full_model <- lm(full_formula, train_data)
step_back_model <- stepAIC(full_model, direction="backward", trsace = F)
poly.call <- summary(step_back_model)$call
final_model <- lm(poly.call[2], train_data)
summary(final_model)

hold_out_data$Prediction <- predict(final_model,hold_out_data)
cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS)

@@

>>>>

#Load in the Data
```{r}
library(tidyverse)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
library(DMwR)
df_train <- read.csv("https://raw.githubusercontent.com/crarnouts/Data_621/master/moneyball-training-data.csv")
df_train$INDEX <- NULL
df_test <- read.csv("https://raw.githubusercontent.com/crarnouts/Data_621/master/moneyball-evaluation-data.csv")
df_test$INDEX <- NULL
source("https://raw.githubusercontent.com/crarnouts/Data_605_Final/master/RandomForestNulls_testing.R")
colnames(df_train) <- sub("TEAM_", "", colnames(df_train))
colnames(df_test) <- sub("TEAM_", "", colnames(df_test))

#Missing Variables 
```{r}
df_train %>% 
  gather(variable, value) %>%
  filter(is.na(value)) %>%
  group_by(variable) %>%
  tally() %>%
  mutate(percent = n / nrow(df_train) * 100) %>%
  mutate(percent = paste0(round(percent, ifelse(percent < 10, 1, 0)), "%")) %>%
  arrange(desc(n)) %>%
  rename(`Variable Missing Data` = variable,
         `Number of Records` = n,
         `Share of Total` = percent) %>%
  kable() %>%
  kable_styling()
```

# See if we can impute some misssing values Using a Random Forest
```{r}

df_train[which(df_train$TARGET_WINS == 0), "TARGET_WINS"] <- round(mean(df_train$TARGET_WINS), 0)

# Change 0's to NA so they too can be imputed
df_train <- df_train %>%
  mutate(BATTING_SO = ifelse(BATTING_SO == 0, NA, BATTING_SO))
knn <- df_train %>% knnImputation()
impute_me <- is.na(df_train$BATTING_SO)
df_train[impute_me,"BATTING_SO"] <- knn[impute_me,"BATTING_SO"]

impute_me <- is.na(df_train$BASERUN_SB)
df_train[impute_me,"BASERUN_SB"] <- knn[impute_me,"BASERUN_SB"]

impute_me <- is.na(df_train$BASERUN_CS)
df_train[impute_me,"BASERUN_CS"] <- knn[impute_me,"BASERUN_CS"]

impute_me <- is.na(df_train$BATTING_HBP)
df_train[impute_me,"BATTING_HBP"] <- knn[impute_me,"BATTING_HBP"]

df_train[which(df_train$PITCHING_SO > 5346),"PITCHING_SO"] <- NA
impute_me <- is.na(df_train$PITCHING_SO)
df_train[impute_me,"PITCHING_SO"] <- knn[impute_me,"PITCHING_SO"]

impute_me <- is.na(df_train$FIELDING_DP)
df_train[impute_me,"FIELDING_DP"] <- knn[impute_me,"FIELDING_DP"]

# Change 0's to NA so they too can be imputed
df_test <- df_test %>%
  mutate(BATTING_SO = ifelse(BATTING_SO == 0, NA, BATTING_SO))
knn <- df_test %>% knnImputation()
impute_me <- is.na(df_test$BATTING_SO)
df_test[impute_me,"BATTING_SO"] <- knn[impute_me,"BATTING_SO"]

impute_me <- is.na(df_test$BASERUN_SB)
df_test[impute_me,"BASERUN_SB"] <- knn[impute_me,"BASERUN_SB"]

impute_me <- is.na(df_test$BASERUN_CS)
df_test[impute_me,"BASERUN_CS"] <- knn[impute_me,"BASERUN_CS"]

impute_me <- is.na(df_test$BATTING_HBP)
df_test[impute_me,"BATTING_HBP"] <- knn[impute_me,"BATTING_HBP"]

df_test[which(df_test$PITCHING_SO > 5346),"PITCHING_SO"] <- NA
impute_me <- is.na(df_test$PITCHING_SO)
df_test[impute_me,"PITCHING_SO"] <- knn[impute_me,"PITCHING_SO"]

impute_me <- is.na(df_test$FIELDING_DP)
df_test[impute_me,"FIELDING_DP"] <- knn[impute_me,"FIELDING_DP"]

@@

#Feature Creation and Data Cleaning

```{r}

df_train$BATTING_1B <- df_train$BATTING_H - df_train$BATTING_2B - df_train$BATTING_3B - df_train$BATTING_HR
df_test$BATTING_1B <- df_test$BATTING_H - df_test$BATTING_2B - df_test$BATTING_3B - df_test$BATTING_HR

#Look at Linear Model with all First Order Predictors
```{r}
train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]
model <- lm(TARGET_WINS ~ ., data = train_data)
hold_out_data$Prediction <- predict(model,hold_out_data)
oos_cor <- paste(round(cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS),digits = 2))
summary(model)

first_order_linear <- ggplot(data = hold_out_data, aes(x = Prediction, y = TARGET_WINS)) + 
  geom_point(color='blue') +
  geom_smooth(method = "lm", se = FALSE)+ggtitle(paste("First Order Linear Model with Out of Sample Correlation of: ",oos_cor))

#Look at some Decision Trees for Variable Interactions
```{r}
hold_out_data <- RF_with_Nulls(train_data,hold_out_data,"TARGET_WINS",1,10,5,.01,5,1)
```

##Look at Variance Inflation Factors 
```{r}
df_train1 <- df_train
# df_train1$BATTING_H <- NULL
# df_train1$BATTING_SO<- NULL
# df_train1$HR_RATIO <- NULL
# df_train1$BASES_ACQUIRED <- NULL
# df_train1$Hitting_Ratio <- NULL
# df_train1$PITCHING_HR <- NULL
for (i in 3:ncol(df_train1)){
col <- noquote(paste(colnames(df_train1)[i],"~ ."))
model <- lm(col, data = df_train1)
r_squared <- summary(model)$adj.r.squared
VIF <- 1/(1-(r_squared))
print(colnames(df_train1)[i])
print(VIF)
#print(summary(model))
}
```

#Stepwise Regression
```{r}

train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]

@@

full_model <- lm(full_formula, train_data)
step_back_model <- stepAIC(full_model, direction="backward", trace = F)
poly.call <- summary(step_back_model)$call
final_model <- lm(poly.call[2], train_data)
summary(final_model)

@@

#Model Results on the Hold Out Dataset
```{r}

hold_out_data$Prediction <- predict(final_model,hold_out_data)

hold_out_data <- hold_out_data %>% filter(Prediction < 182)%>% filter(Prediction > 0)

cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS)

oos_cor <- paste(round(cor(hold_out_data$Prediction,hold_out_data$TARGET_WINS),digits = 2))

ggplotly(ggplot(hold_out_data, aes(x=Prediction, y=TARGET_WINS, colour = TARGET_WINS)) +
     geom_point(shape=1) + 
  scale_color_gradient2(low = "blue",
                             high = "red", space = "Lab" ) +
  geom_smooth(method = "lm", se = FALSE, colour = "orange")+ggtitle(paste("Polynomial Stepwise Model with Out of Sample Correlation of: ",oos_cor))    # Use hollow circles
 )

ggplotly(first_order_linear)
```
